---
title: "Main Function Usage"
author: "Allen Li"
date: "November 25, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(met_hastings)
```

##met_hastings() tutorial

The main function takes in many inputs, which may be confusing at first, so by breaking it down,  
1. nsims - how many trials you need  
2. start - initial estimate  
3. burn_in how many trials to throw away, default = 0  
4. the jumping distribution and its parameters  
5. the sampling distribution and its parameters   
5.5. a function containing your likelihood of your sampling distribution  

A simple example is given as follows:  
Where we are jumping from N$(\theta,2)$
and sampling from $\gamma(\alpha = 1.7, \beta = 4.4)$
```{r}
draws_1 <- met_hastings(nsims = 10000, start = 1, burn_in = 1000, jump = "normal",
jparams = 2,distr = "gamma",c(1.7,4.4))

tail(draws_1)
```

The 95% credible interval can be calculated from those draws as follows:
```{r}
bayes_CI(draws_1,0.1)
```
To demonstrate the usefulness of the Metropolis-Hastings algorithmn, an example with a
sampling distribution that is hard to sample from is presented as follows,
where we are sampling from a mixed gaussian distribution:

```{r}
nn_lk <- function(tstar,params) {
 lkld <- 0.5*rnorm(1,tstar,params[1]) + 0.5*rnorm(1,0,params[2])
}
draws_3 <- met_hastings(nsims = 10000, start = 1, burn_in = 1000,
distr = "custom", dparams = c(1,100) , likelihood = nn_lk)

plot(draws_3, type = "l",main = "Mixed Gaussian", xlab = "Samples", ylab = "#")
```

Performance-wise, the code can sample around 10^5 times without major performance issues, compared to other packages. As detailed in the help document, since there are no comparable rpackages to my knowledge, equivalence is unfortunately not testable. To show that the code is fast for its intended use, a crude performance check is done as follows: 

```{r} 
system.time(met_hastings(nsims = 100000, start = 1, burn_in = 2500,
                          distr = "custom", dparams = c(1,100) , likelihood = nn_lk))
```
